---
title: "Visualizing Starwars characters — Solutions"
author: "Lukas Jürgensmeier"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r load-packages, include=FALSE}
library(tidyverse)
```

### Glimpse at the starwars data frame.

```{r glimpse-starwars}
glimpse(starwars)
```

### Modify the following plot to change the color of all points to `"pink"`.

You can use standard colors by referring to their name, e.g., `colour = "pink"`, or supply a custom Hex color code (e.g., `colour = "#30509C"`).

```{r scatterplot}
ggplot(starwars, 
       aes(x = height, y = mass, color = gender, size = birth_year)) +
  geom_point(color = "pink")
```

### Add labels for title, x and y axes, and size of points. Uncomment to see the effect.

Accurate labels are extremely important to bring across the chart's desired message.
You can specify them within the `labs()` layer.

```{r scatterplot-labels}
ggplot(starwars, 
       aes(x = height, y = mass, color = gender, size = birth_year)) +
  geom_point(color = "#30509C") +
  labs(
    title = "Height vs. Mass of Starwars Characters",
    subtitle = "by birth year",
    x = "Mass (kg)",
    y = "heigth (cm)",
    size = "Birth year",
    caption = "Source: The Star Wars API (swapi.dev)"
    )
```

### Pick a single categorical variable from the data set and make a bar plot of its distribution.

This sample solution provides the easiest possible solution and a more advanced one.
Note the huge difference between the ease of understanding the data.

The simplest possible barplot, which is hard to understand:

```{r barplot1}
ggplot(starwars, aes(y = hair_color)) +
  geom_bar()
```

And in comparison, a little more advanced barplot (note that I'm using functions and tools that will be introduced later in this course):

```{r barplot2}
starwars %>% 
  # reorders the hair color variable by descending frequency
  mutate(hair_color = fct_rev(fct_infreq(hair_color))) %>% 
  # start plotting
  ggplot(aes(y = hair_color)) +
  # common pitfall: use `fill =` instead of `color =`
  geom_bar(fill = "#30509C") +
  labs(
    title = "Do most Starwars characters have no hair?",
    subtitle = "...or are those missing values?",
    x = "Number of Starwars characters",
    y = "Hair color",
    caption = "Source: The Star Wars API (swapi.dev)"
    )
```

### Pick a single numerical variable and make a histogram of it.

We didn't cover histograms specifically, but the code structure is the same.

```{r histogram}
ggplot(starwars, aes(x = mass)) +
  geom_histogram(fill = "#30509C", binwidth = 20) +
  labs(
    title = "Whose the outlier?",
    subtitle = "Mass distribution of starwars characters",
    x = "Mass (kg)",
    y = "Number of starwars characters",
    caption = "Source: The Star Wars API (swapi.dev)"
    )

ggplot(starwars, aes(x = birth_year)) +
  geom_histogram(fill = "#30509C", binwidth = 20) +
  labs(
    title = "Who are the outlier?",
    subtitle = "Birth year distribution of starwars characters",
    x = "Birth year",
    y = "Number of starwars characters",
    caption = "Source: The Star Wars API (swapi.dev)"
    )
```
